14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-07-04 rules/rules19.tex
Rules: Refine competition-wide recognitions.

The sequential score for a division is computed for \emph{all} tracks
\emph{except} the \inctrack and incremental benchmarks in the
\challtrack\footnote{Since incremental track benchmarks may be partially
solved, defining a useful sequential performance for the incremental track
would require information not provided by the parallel performance, e.g.,
detailed timing information for each result.}.  It is defined for a
participating solver in a division with $M$ benchmarks as the sum of all the
individual sequential benchmark scores:
$$\sum_{b\in M} \langle e_{S_b}, n_{S_b}, w_{S_b}, c_{S_b}\rangle$$.

\noindent
A sequential division score $\langle e_S, n_S, c_S\rangle$ is better than a
sequential division score $\langle e_S', n_S', c_S'\rangle$ iff $e_S < e_S'$ or
($e_S = e_S'$ and $n_S > n_S'$) or ($e_S = e_S'$ and $n_S = n_S'$ and $c_S <
c_S'$).  That is, fewer errors takes precedence over more correct solutions,
which takes precedence over less CPU time taken.

@@

Let $n_i^D$ be the correctness score of the $i$th solver (for a given scoring system e.g. number of correct results or reduction) in division $D$. The rank of division $D$ is given as
\[
\frac{n_1^D+1}{n_2^D+1}
\]
The \emph{biggest lead winner} is the winner of the division with the highest (largest) rank. This can be computed per scoring system.

@@

Let $\langle e_b^s, n_b^s, w_b^s, c_b^s \rangle$ be the parallel benchmark score for benchmark $b$ and solver $s$ (for a given scoring system e.g. $n$ is either number of correct results or reduction). 
The virtual best solver score for a division $D$ using solvers $S$ is given as 
\[
\mathit{vbss}(D,S) = \sum_{b \in D} {\sf min}\{ n_b^s \times c_b^s \mid s \in S ~\mathit{and}~ n_b^s > 0  \}
\]
where the minimum of an empty set is 0 (e.g. no contribution if a benchmark is unsolved). In other words, for the single query track, $\mathit{vbss}(D,S)$ is the smallest amount of time taken to solve all benchmarks solved in division $D$ using solvers in $S$.

Let $S$ be the set of competitive solvers competing in division $D$. The rank of solver $s \in S$ in division $D$ is then
\[
1- \frac{\mathit{vbss}(D,S-s) }{ \mathit{vbss}(D,S)}
\]
e.g. the difference in virtual best solver score when removing $s$ from the computation. This will be a number between 0 and 1 with 0 indicating that $s$ made no impact on the \emph{vbss} and 1 indicating that $s$ is the only solver that solved anything in the division. 
%
The \emph{largest contribution winner} is the solver across all divisions with the highest (largest) rank. Again, this can be computed per scoring system.

>>>>

The sequential score for a division is computed for \emph{all} tracks
\emph{except} the \inctrack and incremental benchmarks in the
\challtrack\footnote{Since incremental track benchmarks may be partially
solved, defining a useful sequential performance for the incremental track
would require information not provided by the parallel performance, e.g.,
detailed timing information for each result.}.  It is defined for a
participating solver in a division with $M$ benchmarks as the sum of all the
individual sequential benchmark scores:
$$\sum_{b\in M} \langle e_b^s, n_b^s, w_b^s, c_b^s\rangle$$.

\noindent
A sequential division score $\langle e^s, n^s, c^s\rangle$ is better than a
sequential division score $\langle e^{s'}, n^{s'}, c^{s'}\rangle$ iff
$e^s < e^{s'}$ or ($e^s = e^{s'}$ and $n^s > n^{s'}$) or ($e^s = e^{s'}$ and
$n_S = n^{s'}$ and $c^s < c^{s'}$).
That is, fewer errors takes precedence over more correct solutions,
which takes precedence over less CPU time taken.

@@

Let $n_i^D$ be the correctness score of the $i$th solver (for a given scoring
system e.g. number of correct results or reduction) in division $D$.
The \emph{correctness rank} of division $D$ is given as
\[
\frac{n_1^D+1}{n_2^D+1}
\]
Let $c_i^D$ be the CPU time score of the $i$th solver in division $D$.
The \emph{CPU time rank} of division $D$ is given as
\vspace{-1ex}
\[
\frac{c_2^D+1}{c_1^D+1}
\]
Let $w_i^D$ be the wall-clock time score of the $i$th solver in division $D$.
The \emph{wall-clock time rank} of division $D$ is given as
\vspace{-1ex}
\[
\frac{w_2^D+1}{w_1^D+1}
\]
The \emph{biggest lead winner} is the winner of the division with the highest
(largest) correctness rank. In case of a tie, the winner is determined as the
solver with the higher corresponding CPU (resp. wall-clock) time rank for
sequantial (resp. parallel) scoring.
This can be computed per scoring system.

@@

Let $\langle e^s, n^s, w^s, c^s \rangle$ be the parallel division score
for solver $s$ (for a given scoring system, i.e., $n$ is either number of correct
results or reduction).
If the division error score $e^s > 0$, then solver $s$ is considered unsound
and excluded from the ranking.
If the number of sound competitive solvers~$S$ in a division $D$ is $|S| < 2$, 
the division is excluded from the ranking.

Let $\langle e_b^s, n_b^s, w_b^s, c_b^s \rangle$ be the parallel benchmark
score for benchmark $b$ and solver $s$ (for a given scoring system). 
The virtual best solver \emph{correctness score} for a division $D$ with 
competitive sound solvers $S$ is given as 
\[
\mathit{vbss}_n(D,S) = \sum_{b \in D} {\sf max}\{ n_b^s \mid s \in S ~\mathit{and}~ n_b^s > 0 \}
\]
where the maximum of an empty set is 0 (i.e., no contribution if a benchmark
is unsolved).

The virtual best solver \emph{CPU time score} $\mathit{vbss}_c$ and
the virtual best solver \emph{wall-clock time score} $\mathit{vbss}_w$ for a
division $D$ with competitive sound solvers $S$ is given as 
\[
\mathit{vbss}_c(D,S) = \sum_{b \in D} {\sf min}\{ c_b^s \mid s \in S ~\mathit{and}~ n_b^s > 0 \}
\]
\[
\mathit{vbss}_w(D,S) = \sum_{b \in D} {\sf min}\{ w_b^s \mid s \in S ~\mathit{and}~ n_b^s > 0 \}
\]
where the minimum of an empty set is 2400 seconds
(no solver was able to solve the benchmark).

In other words, for the single query track,
$\mathit{vbss}_c(D,S)$  and $\mathit{vbss}_w(D,S)$ is the
smallest amount of CPU time and wall-clock time taken to solve all benchmarks
solved in division $D$ using all sound competitive solvers in $S$.

Let $S$ be the set of competitive solvers competing in division $D$.
The \emph{correctness rank} $\mathit{vbss}_n$, the \emph{CPU time rank}
$\mathit{vbss}_c$ and the \emph{wall-clock time rank} $\mathit{vbss}_w$
of solver $s \in S$ in division $D$ are then defined as
\[
1- \frac{\mathit{vbss}_n(D,S-s) }{ \mathit{vbss}_n (D,S)}
\hspace{3em}
1- \frac{\mathit{vbss}_c(D,S) }{ \mathit{vbss}_c(D,S-s)}
\hspace{3em}
1- \frac{\mathit{vbss}_w(D,S) }{ \mathit{vbss}_w(D,S-s)}
\]
i.e., the difference in virtual best solver score when removing $s$ from the
computation.

These ranks will be numbers between 0 and 1 with 0 indicating that $s$ made no
impact on the \emph{vbss} and 1 indicating that $s$ is the only solver that
solved anything in the division.
%
The ranks for a division $D$ in a given track will be normalized by multiplying
with $\frac{n_D}{N}$, where $n_D$ corresponds to the number of competitive
solver/benchmark pairs in division $D$ and $N$ being the overall number of
competitive solver/benchmark pairs of this track.

The \emph{largest contribution winner} is the solver across all divisions with
the highest (largest) normalized correctness rank. Again, this can be computed
per scoring system. In case of a tie, the winner is determined as the solver
with the higher corresponding normalized CPU (resp. wall-clock) time rank for
sequential (resp. parallel) scoring.
